\tcode{Generalisation of nth_element to a range of nths}

### 2022-01-09 draft_lundberg_nth_elements.tex
updated performance image

\begin{tabular}{ll}
Document \#:& D2375R1\\
Date: &2022-01-02 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

2021-12-16: Added clarifications and more background, explanations, wording clarifications, references, summarized performance study, applications, more questions/answers. --Based on feedback and material sent to SG9 list 2021-12-09. Added images for equalization example. Added example of \emph{Before} with projections and more examples. -- 
2021-12-26: Added explanatory images to the introduction. --  
2021-12-28: Rebased wording and synopsis to C++23 draft. 2021-01-02: Updated to new performance result. Clarified that complexity is expected. Misc polishing.

@@

\newpage
\section{The algorithm}
\label{Implementation}
\label{Implement}

@@

\begin{center}
\includegraphics[width=0.55\textwidth]{plotting/images/mqs_med3_equi_speed_for_n_vs_sort.png}
\end{center}

@@

\begin{center}
\begin{tabular}{|r|c|c|} %
  \hline 
  \textbf{m} & \textbf{speedup factor} & \textbf{at N}\\
  \hline 
1 & 10 & $N=3e7$\\
5 & 5 & $N=3e7$\\
10 & 4.5 & $N=3e7$\\
500 & 2.3 & $N=3e7$\\
1000 & 2.1 & $N=3e7$\\
\hline
10 & 3.6 & $N=3e5$\\
50 & 2.4 & $N=3e5$\\
\hline
5 & 2.6 & $N=3e3$\\
  \hline 
\end{tabular}
\end{center}

>>>>

\begin{tabular}{ll}
Document \#:& D2375R1\\
Date: &2022-01-09 \\
Project: & Programming Language C++ \\
Audience: & LEWG, SG9 \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

2021-12-16: Added clarifications and more background, explanations, wording clarifications, references, summarized performance study, applications, more questions/answers. --Based on feedback and material sent to SG9 list 2021-12-09. Added images for equalization example. Added example of \emph{Before} with projections and more examples. -- 
2021-12-26: Added explanatory images to the introduction. --  
2021-12-28: Rebased wording and synopsis to C++23 draft. 2021-01-02: Updated to new performance result. Clarified that complexity is expected. Misc polishing. 2022-01-09: Updated performance figure.

@@

\newpage
\section{Algorithm Implementation}
\label{Implementation}
\label{Implement}

@@

\begin{center}
\includegraphics[width=0.55\textwidth]{plotting/images/multiselect_equi_speed_for_n_vs_sort.pdf}
\end{center}

@@

\begin{center}
\begin{tabular}{|r|c|c|} %
  \hline 
  \textbf{m} & \textbf{speedup factor} & \textbf{at N}\\
  \hline 
1 & 11 & $N=3e7$\\
5 & 5.7 & $N=3e7$\\
10 & 4.7 & $N=3e7$\\
500 & 2.3 & $N=3e7$\\
1000 & 2.2 & $N=3e7$\\
\hline
10 & 3.6 & $N=3e5$\\
50 & 2.5 & $N=3e5$\\
\hline
5 & 2.6 & $N=3e3$\\
  \hline 
\end{tabular}
\end{center}
